---
title: "topic_7_assignment"
author: "Connor Flynn"
date: "5/31/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(here)
library(tidytext)
library(tidyverse)
library(widyr)
library(irlba) #singluar value decomposition
library(broom) # creating search_synonym function
library(textdata)
library(ggplot2)
library(dplyr)
```

```{r, include=FALSE}
data <- read_table(file = here("data/glove.6B/glove.6B.300d.txt"),
                   col_names = FALSE)
```


1.  Recreate the analyses in the last three chunks (find-synonyms, plot-synonyms, word-math) with the GloVe embeddings. How are they different from the embeddings created from the climbing accident data? Why do you think they are different?

```{r, include=FALSE}
data <- data %>% 
  column_to_rownames(var = "X1")
  
```

```{r}
word_vectors <- as.matrix(data)
```

```{r}
search_synonyms <- function(word_vectors, selected_vector) {
dat <- word_vectors %*% selected_vector
    
similarities <- dat %>%
        tibble(token = rownames(dat), similarity = dat[,1])
similarities %>%
       arrange(-similarity) %>%
        select(c(2,3))
}
```


```{r}
fall <- search_synonyms(word_vectors,word_vectors["fall",])
slip <- search_synonyms(word_vectors,word_vectors["slip",])
```

```{r plot-synonyms}
slip %>%
    mutate(selected = "slip") %>%
    bind_rows(fall %>%
                  mutate(selected = "fall")) %>%
    group_by(selected) %>%
    top_n(15, similarity) %>%
    ungroup %>%
    mutate(token = reorder(token, similarity)) %>%
    ggplot(aes(token, similarity, fill = selected)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~selected, scales = "free") +
    coord_flip() +
    theme(strip.text=element_text(hjust=0, size=12)) +
    scale_y_continuous(expand = c(0,0)) +
    labs(x = NULL, title = "What word vectors are most similar to slip or fall?")
         
```

The synonyms here are different from the climbing data due to the nature of the datset. Here, it appears that the term 'fall' is in a financial context. 'Slip' seems to appear in a sporting context. It would be useful to eliminate tenses of the two terms to get a clearer analysis. 



2.  Run the classic word math equation, "king" - "man" = ?

```{r}
king_man <- word_vectors["king",] - word_vectors["man",] 
search_synonyms(word_vectors, king_man)
```


3.  Think of three new word math equations. They can involve any words you'd like, whatever catches your interest.



```{r}
indigenous_knowledge <- word_vectors["indigenous",] - word_vectors["knowledge",] 
search_synonyms(word_vectors, indigenous_knowledge)
```

```{r}
polynesian_islands <- word_vectors["polynesian",] - word_vectors["islands",] 
search_synonyms(word_vectors, polynesian_islands)
```

```{r}
music_culture <- word_vectors["music",] - word_vectors["culture",] 
search_synonyms(word_vectors, music_culture)
```

